The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-03-24 paper/authors.tex
add initial
adding my affiliation and orcid

\author[0000-0002-3065-457X]{Peter Hatfield}
\affiliation{Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}

\author[0000-0001-9298-3523]{Kartheik Iyer}
\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St George St, Toronto, ON M5S 3H4, Canada}

@@

\author{Alex Malz}
\affiliation{Ruhr University Bochum, Faculty of Physics and Astronomy, Astronomical Institute (AIRUB), German Centre for Cosmological Lensing, 44780 Bochum, Germany}

>>>>

\author{Peter Hatfield}
\noaffiliation

\author{Kartheik Iyer}
\noaffiliation

@@

\author[0000-0002-8676-1622]{Alex I. Malz}
\affiliation{German Centre of Cosmological Lensing, Ruhr-Universit\"{a}t, Universit\"{a}tsstra{\ss}e 150, 44801 Bochum, Germany}
